% publications

% notes:
% I'd like a way to turn on/off the acceptance rates
\section{Publications}
\subsection{Journals}
% this part copied from the bbl file
\begin{thebibliography}{3}
\bibitem{prk_zhang_tosn13}
%Hongwei Zhang, Xin Che, \bibauthor{Xiaohui Liu}, Xi Ju
Hongwei Zhang, Xin Che, Xiaohui Liu, Xi Ju.
\\ \newblock \emph{Adaptive Instantiation of the Protocol Interference Model in Wireless Networked Sensing and Control}.
\\ \newblock In \emph{\textbf{ACM Transactions on Sensor Networks (ToSN)}, Volume 10 Issue 2, Article No. 28, January 2014.}

\bibitem{mta_liu_tsg12}
Xiaohui Liu, Hongwei Zhang, Qiao Xiang, Xin Che, Xi Ju.
\\ \newblock \emph{Taming Uncertainties in Real-Time Routing for Wireless Networked Sensing and Control}.
\\ \newblock In \emph{\textbf{IEEE Transactions on Smart Grid (TSG)}, special issue on “Smart Grid Communication Systems: Reliability, Dependability, and Performance", Vol. 4, No. 1, March 2013.}

\bibitem{tpack_xiang_tmc11}
Qiao Xiang, Jinhong Xu, Xiaohui Liu, Hongwei Zhang, Loren J. Rittle.
\\ \newblock \emph{When In-Network Processing Meets Time: Complexity and Effects of Joint Optimization in Wireless Sensor Networks}.
\\ \newblock In \emph{\textbf{IEEE Transactions on Mobile Computing (TMC)}, 10(10), pp. 1488-1502, October 2011.}

\end{thebibliography}


\subsection{Conferences \& Workshops}
% this part copied from the bbl file
\begin{thebibliography}{4}
\bibitem{mta_liu_mobihoc12}
Xiaohui Liu, Hongwei Zhang, Qiao Xiang, Xin Che, Xi Ju.
\\ \newblock \emph{Taming Uncertainties in Real-Time Routing for Wireless Networked Sensing and Control}.
\\ \newblock In \emph{\textbf{13th ACM International Symposium on Mobile Ad Hoc Networking and Computing (MobiHoc)}, 2012.}

\bibitem{mta_liu_realwin11}
Xiaohui Liu, Hongwei Zhang, Qiao Xiang.
\\ \newblock \emph{Towards Predictable Real-Time Routing for Wireless Networked Sensing and Control}.
\\ \newblock In \emph{\textbf{Cyber-Physical-Systems (CPS) Week Workshop on Real-Time Wireless for Industrial Applications (RealWin)}, 2011.}

\bibitem{prk_xin_secon10}
Xin Che, Xiaohui Liu, Xi Ju, Hongwei Zhang.
\\ \newblock \emph{Adaptive Instantiation of the Protocol Interference Model in Mission-Critical Wireless Networks}.
\\ \newblock In \emph{\textbf{7th IEEE Communications Society Conference on Sensor, Mesh and Ad Hoc Communications and Networks (SECON)}, 2010.}

\bibitem{mta_xiang_rtss11}
Qiao Xiang, Jinhong Xu, Xiaohui Liu, Hongwei Zhang, Loren J. Rittle.
\\ \newblock \emph{When In-Network Processing Meets Time: Complexity and Effects of Joint Optimization in Wireless Sensor Networks}.
\\ \newblock In \emph{\textbf{30th IEEE Real-Time Systems Symposium (RTSS)}, 2009.}

\end{thebibliography}


\subsection{Posters \& Demos}
\begin{thebibliography}{1}
\bibitem{prks_zhang_iccpsposter13}
Hongwei Zhang, Xiaohui Liu, Chuan Li, Yu Chen, Xin Che, Feng Lin, Le Yi Wang, George Yin.
\\ \newblock \emph{Poster Abstract: PRK-Based Scheduling for Predictable Link Reliability in Wireless Networked Sensing and Control}.
\\ \newblock In \emph{\textbf{4th ACM/IEEE International Conference on Cyber-Physical Systems (ICCPS)}, 2013}

\end{thebibliography}

\subsection{Technical Reports}
\begin{thebibliography}{4}
\bibitem{prks_zhang_tr}
H. Zhang, C. Li, X. Liu, Y. Chen, X. Che, F. Lin, L. Y. Wang, and G. Yin.
\\ \newblock \emph{PRK-based scheduling for predictable link reliability in wireless networked sensing and control}.
\\ \newblock In \emph{\textbf{Technical Report DNC-TR-14-01, Wayne State University}, 2014.}

\bibitem{prk_zhang_tr}
H. Zhang, X. Che, X. Liu, and X. Ju.
\\ \newblock \emph{Adaptive instantiation of the protocol interference model in wireless networked sensing and control}.
\\ \newblock In \emph{\textbf{Technical Report WSU-CS-DNC-TR-12- 01, Wayne State University}, 2012.}

\bibitem{mta_xiaohui_tr}
X. Liu, H. Zhang, Q. Xiang, X. Che, and X. Ju.
\\ \newblock \emph{Taming uncertainties in real-time routing for wireless networked sensing and control}.
\\ \newblock In \emph{\textbf{Technical Report DNC-TR-11-04, Wayne State University}, 2011}

\bibitem{tpack_zhang_tr}
Q. Xiang, J. Xu, X. Liu, H. Zhang, and L. J. Rittle.
\\ \newblock \emph{When in-network processing meets time: Complexity and effects of joint optimization in wireless sensor networks}.
\\ \newblock In \emph{\textbf{Technical Report DNC-TR-09-01, Wayne State University}, 2009.}
\end{thebibliography}

\subsection{Under Review}
%\subsection{In Preparation}
\begin{thebibliography}{3}
\bibitem{prks_zhang_mobihoc14}
Hongwei Zhang, Xiaohui Liu, Chuan Li, Yu Chen, Xin Che, Feng Lin, Le Yi Wang, George Yin.
\\ \newblock \emph{PRK-Based Scheduling for Predictable Link Reliability in Wireless Networked Sensing and Control}.
\\ \newblock In \emph{\textbf{The 14th International Conference on Information Processing in Sensor Networks (IPSN)}, 2015.}

\bibitem{onama_liu_globecom14}
Xiaohui Liu, Hongwei Zhang.
\\ \newblock \emph{A Maximal Concurrency and Low Latency Distributed Scheduling Protocol for Wireless Sensor Networks}.
\\ \newblock In \emph{\textbf{IEEE Wireless Communications and Networking Conference (WCNC)}, 2015.}

\bibitem{rts_liu_rtas14}
Xiaohui Liu, Hongwei Zhang.
\\ \newblock \emph{Real-Time Convergecast Scheduling in Lossy Multi-hop Wireless Sensor Networks}.
\\ \newblock In \emph{\textbf{12th IEEE Communications Society Conference on Sensor, Mesh and Ad Hoc Communications and Networks (SECON)}, 2015}

\end{thebibliography}
